Practice handling data 1 - 02.10.24

### 2024-10-02 datapractice1.Rmd
datapracticew5

---
title: "Week 5  - Chapter 7 pt. 2 - Analysis"
author: "Verooo"
date: "2024-10-02"
output: html_document
---

@@

# 7.10 Step 1: Define Data
```{r}

str(test$nets)
length(test$nets)
dim(test$nets)

@@

```{r}
wave1 <- test$nets[1,,]
wave2 <- test$nets[2,,]

# let us put the diagonal to zero
diag(wave1) <- 0
diag(wave2) <- 0
# we want a binary tie (not a weighted tie)
wave1[wave1 > 1] <- 1
wave2[wave2 > 1] <- 1
# put the nets in an array
net_soc_array <- array(data = c(wave1, wave2), dim = c(dim(wave1), 2))
str(net_soc_array) #now we basically restructured this 
# dependent
net <- sienaDependent(net_soc_array)
```

# 7.11 Step 2: Create effects structure

# didnt' make the IV gender butif i Had: mydata <- sienaDataCreate(net, gender)

#for now we will do it without
mydata <- sienaDataCreate(net)     #effects based on your data (here reciprocity and degree only)

myeff <- getEffects(mydata)
# effectsDocumentation(myeff)    #if you run this part you are told whihc ones are POSSIBLE

```
THIS IS ALL THE EFFECTS YOU COULD LOOK AT IN YOUR NETWORK 
e.g. outdegree (density), called density, three things: evaluation, endowment, and creation
  you can only include two of the three (tie creation, breaking and maintaining)
  Assumption meachnisms to make and breka a tie are the same so we only use the EVALUATION part

  All these effects are describedin the manual of RSiena Chapter 12 (9?)

# 7.12 Step 3: Get initial description

```{r}
ifelse(!dir.exists("results"), dir.create("results"), FALSE)
#if there is not a folder called "results" in your repository: make one
```

```{r}
print01Report(mydata, modelname = "./results/soc_init") # create file with report in results folder 
```
 Has a lot of information in there 
 Also: how tie CHANGED 
    Also: Jaccard index (measure of stability)
 Also rate parameter and outdegree

# 7.13 STEP 4: Specify model 
Sometimes similartostep 2 (but here you include specifically the effects you want to look at)
```{r}
# if you want to select only specific effects in your model:

myeff <- includeEffects(myeff, isolateNet, inPop, outAct)  #we know that quite a lot of staff has not published with someone else

```
inpope ppl with lots of indegrees will havelotof indegrees later (in population)
 outAct ppl with lots of outdegrees will have lot of indegrees later

 hint for my own project: interaction effect of these statistics and the effect of gender

# myeff <- includeEffects(myeff, sameX, egoX, altX, interaction1 = "gender")

```
altX 
egos send more ties who have more on gender (aka. gender =1)

egoX
[definition?]

 "interaction1" HAS NOTHING TO DO WITH AN INTERACTION EFFECT

# 7.14 STEP 5: Estimate model 
```{r}
myAlgorithm <- sienaAlgorithmCreate(projname = "soc_init")
ansM1 <- siena07(myAlgorithm, data = mydata, effects = myeff, returnDeps = TRUE)

# if necessary estimate again!  ansM1 <- siena07(myAlgorithm, data = mydata, effects = myeff,
# prevAns = ansM1, returnDeps=TRUE)

ansM1  # shortfor answers model 1
```
convergence ratio should be <.25

# 7.15 Step 6: GOF (goodness of fit) - next week

---

# Sidenote: H- index via openAlex

Hirsch-Index is NOT scraped in open-alex already but you have the nr. of citations and you can google how someone else did it

# STUDY CHAPTER 12 of RSiena Manual!

>>>>

---
title: "Practice handling data 1 - 02.10.24"
author: "Verooo"
date: "2024-10-02"
output: html_document
---

@@

```{r}
nets <- test$nets

df_ego_demo <- test$data$demographics
df_ego_oa <- test$data$scholars_oa
df_ego_works <- test$data$works

# str(df_ego_demo, 1)
# df_ego_demo[[1]]

df_ego_demo <- do.call(rbind.data.frame, df_ego_demo)

str(df_ego_oa, 1)
df_ego_oa[[1]]

df_ego_oa <- do.call(rbind.data.frame, df_ego_oa)

?join.data.frame
df_ego <- left_join(df_ego_demo, df_ego_oa, by = join_by(au_id == id))

#yes, the correct ones!!!
rownames(nets[1,,]) == df_ego$au_id

df_ego_works[[1]]$author
df_ego$Naam
# df_ego$gender <- c(1,0,1,1) # manually fill in gender

@@
